---
title: 'r4ds Chapter 3'
author: "Smiti Kaul"
date: "Jan 22 - Feb 1, 2018"
output: 
  pdf_document: 
    highlight: pygments

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(grid)
library(langdata)
data(swda); data(brown)
```

# Modify SWDA data
```{r}
df <- swda
df$sex[df$sex == 'MALE'] <- 0
df$sex[df$sex == 'FEMALE'] <- 1

# sort(unique(df$dialect_area))
df$dialect_area[df$dialect_area == 'MIXED'] <- 0
df$dialect_area[df$dialect_area == 'NEW ENGLAND'] <- 1
df$dialect_area[df$dialect_area == 'NORTH MIDLAND'] <- 2
df$dialect_area[df$dialect_area == 'NORTHERN'] <- 3
df$dialect_area[df$dialect_area == 'NYC'] <- 4
df$dialect_area[df$dialect_area == 'SOUTH MIDLAND'] <- 5
df$dialect_area[df$dialect_area == 'SOUTHERN'] <- 6
df$dialect_area[df$dialect_area == 'UNK'] <- 7
df$dialect_area[df$dialect_area == 'WESTERN'] <- 8

df$sex <- as.numeric(as.character(df$sex))
df$dialect_area <- as.numeric(as.character(df$dialect_area))
df$utterance_num <- as.numeric(as.character(df$utterance_num))
df$turn_num <- as.numeric(as.character(df$turn_num))
```

# 3.2: First steps
```{r, fig.asp = 0.4}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
ggplot(data = df) + geom_point(mapping = aes(x = birth_year, y = turn_num))
ggplot(data = df) + geom_point(mapping = aes(x = utterance_num, y = turn_num))

ggplot(data = df) + geom_point(mapping = aes(x = dialect_area, y = utterance_num))
ggplot() + geom_point(data = df, mapping = aes(x = dialect_area, y = utterance_num))

plot(utterance_num ~ dialect_area, data = df)

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

## Exercises

```{r, eval = FALSE}
dim(mpg) # 234 rows, 11 columns
```

drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

```{r}
p1 = ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))
p2 = ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
grid.arrange(p1, p2, ncol = 2)
```

Not useful because we can't see any patterns due to few data points?

# 3.3: Aesthetic Mappings

```{r}
p1 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

p2 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

p3 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

p4 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))

p5 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

pushViewport(viewport(layout = grid.layout(2, 2)))
print(p1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p2, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(p3, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(p4, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
show(p5)
```

## Exercises

1. The correct code is $ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")$.

2. categorical vs. continuous

3. 

4. 

5. stroke: to modify the width of the border of a shape with a border

6. 

# 3.4: Common problems

# 3.5: Facets

A facet is a subplot that displays one subset of the data. 

```{r, fig.asp = 0.5}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

facet_grid() to facet my plot on the combo of two variables.

```{r, fig.asp = 0.5}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
# facet_grid(. ~ cyl) if you prefer to not facet in the rows of columns direction
```

## Exercises
1. 
2. 
3.
```{r, fig.asp = 0.5}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
 facet_grid(drv ~ .)

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

4.
```{r, fig.asp = 0.5}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```

# 3.6: Geometric objects

# 3.7: Statistical transformations

```{r, fig.asp = 0.5}
ggplot(data = df) + geom_bar(mapping = aes(x = dialect_area)) + labs(title = 'dialect_area counts')
ggplot(data = swda) + geom_bar(mapping = aes(x = dialect_area)) + labs(title = 'dialect_area counts')
ggplot(data = df) + geom_bar(mapping = aes(x = dialect_area, y = utterance_num), stat = "identity") + labs(title = 'dialect_area ~ utterance_count')

ggplot(df, aes(dialect_area, ..count..)) + geom_bar(aes(fill = utterance_num), position = "dodge")
ggplot(swda, aes(sex, ..count..)) + geom_bar(aes(fill = utterance_num), position = "dodge")
ggplot(swda, aes(utterance_num, ..count..)) + geom_bar(aes(fill = sex), position = "dodge")
```


# 3.8: Position adjustments

# 3.9: Coordinate systems

# 3.10: 


