---
title: 'r4ds Chapter 3'
author: "Smiti Kaul"
date: "Jan 22 - Feb 1, 2018"
output: 
  pdf_document: 
    highlight: pygments

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(grid)
```

# 3.2: First steps
```{r, fig.asp = 0.4}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```

## Exercises

```{r, eval = FALSE}
dim(mpg) # 234 rows, 11 columns
```

drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

```{r}
p1 = ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))
p2 = ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
grid.arrange(p1, p2, ncol = 2)
```

Not useful because we can't see any patterns due to few data points?

# 3.3: Aesthetic Mappings

```{r}
p1 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

p2 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

p3 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

p4 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))

p5 = ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

pushViewport(viewport(layout = grid.layout(2, 2)))
print(p1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p2, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(p3, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(p4, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
show(p5)
```

## Exercises

1. The correct code is $ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")$.

2. categorical vs. continuous

3. 

4. 

5. stroke: to modify the width of the border of a shape with a border

6. 

# 3.4: Common problems

# 3.5: Facets

A facet is a subplot that displays one subset of the data. 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

facet_grid() to facet my plot on the combo of two variables.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
# facet_grid(. ~ cyl) if you prefer to not facet in the rows of columns direction
```

## Exercises
1. 
2. 
3.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
 facet_grid(drv ~ .)

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

4.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```

# 3.6: Geometric objects

# 3.7: Statistical transformations

# 3.8: Position adjustments

# 3.9: Coordinate systems

# 3.10: 


