---
title: 'Test Mining with R'
author: "Smiti Kaul"
date: "Feb 9 - present, 2018"
output: 
  pdf_document: 
    highlight: pygments

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, tidy = TRUE}
if (!require("pacman", character.only = TRUE)) {
  install.packages("pacman")
  library("pacman", character.only = TRUE)
}
pacman:: p_load(scales, wordcloud, reshape2, tidyverse, ggplot2, gridExtra, grid, langdata, gutenbergr, tidytext, janeaustenr, stringr, dplyr, tm, topicmoddels)
# data(swda); data(brown); data(stop_word)
```

## Following the article
```{r, tidy = TRUE, eval = FALSE}
ids <- 1:5
works_sample <- gutenberg_download(gutenberg_id = ids)
glimpse(works_sample)
names(gutenberg_metadata)
works_sample <- gutenberg_download(gutenberg_id = ids, meta_fields = c("title", "author"))
glimpse(works_sample)
ids <- filter(gutenberg_subjects, subject_type == "lcc", subject == "PR")
glimpse(ids)
ids_has_text <- filter(gutenberg_metadata, gutenberg_id %in% ids$gutenberg_id, has_text == TRUE)
glimpse(ids_has_text)

set.seed(123)
ids_sample <- sample_n(ids_has_text, 10)
glimpse(ids_sample)
works_pr <- gutenberg_download(gutenberg_id = ids_sample$gutenberg_id, meta_fields = c("author", "title"))
glimpse(works_pr)
```

## Getting Started
```{r, tidy = TRUE, echo = FALSE}
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")
text
text_df <- data_frame(line = 1:4, text = text)
text_df
text_df %>% unnest_tokens(word, text)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books

tidy_books <- original_books %>%
  unnest_tokens(word, text) %>% 
  anti_join(stop_words)

tidy_books %>% count(word, sort = TRUE) %>% 
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

## Gutenberg: tidy text format
```{r, tidy = TRUE}
hgwells <- gutenberg_download(c(35, 36, 5230, 159))
bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) 

tidy_hgwells %>% count(word, sort = TRUE)

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_bronte %>% count(word, sort = TRUE)

frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"),
                       mutate(tidy_hgwells, author = "H.G. Wells"), 
                       mutate(tidy_books, author = "Jane Austen")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(author, proportion) %>% 
  gather(author, proportion, `Brontë Sisters`:`H.G. Wells`)

# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = `Jane Austen`, color = abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Jane Austen", x = NULL)

cor.test(data = frequency[frequency$author == "Brontë Sisters",],
         ~ proportion + `Jane Austen`);

cor.test(data = frequency[frequency$author == "H.G. Wells",], 
         ~ proportion + `Jane Austen`);
```

## Sentiment Analysis

```{r, tidy = TRUE}
nrcjoy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE)

janeaustensentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

ggplot(janeaustensentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

### Most common positive and negative words
```{r, tidy = TRUE}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts

bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()

# add 'miss' as a custom stop word
custom_stop_words <- bind_rows(data_frame(word = c("miss"), 
                                          lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```

### Wordclouds
```{r, tidy = TRUE}
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

### Units beyond just words

## Word and Document Frequency

### Term Frequency
```{r, tidy = TRUE}
book_words <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE) %>%
  ungroup()

total_words <- book_words %>% 
  group_by(book) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)

head(book_words)

ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```

### Zipf's Law
```{r, tidy = TRUE}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)

head(freq_by_rank)

freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

### The bind_tf_idf function
```{r, tidy = TRUE}
book_words <- book_words %>%
  bind_tf_idf(word, book, n)
head(book_words)

book_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))

book_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(book) %>% 
  top_n(15) %>% 
  ungroup %>%
  ggplot(aes(word, tf_idf, fill = book)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~book, ncol = 2, scales = "free") +
  coord_flip()
```

### A corpus of physics texts
```{r, tidy = TRUE}
physics <- gutenberg_download(c(37729, 14725, 13476, 5001), 
                              meta_fields = "author")
```

```{r, tidy = TRUE}
physics_words <- physics %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

head(physics_words)

plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan", 
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

plot_physics %>% 
  group_by(author) %>% 
  top_n(15, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free") +
  coord_flip()
```

### A corpus of ___ texts
```{r, tidy = TRUE}
# gutenberg_metadata %>% filter(title == "Ramayana, English")
bib <- gutenberg_download(10, meta_fields = "author")
anthem <- gutenberg_download(1249, meta_fields = "author")
sid <- gutenberg_download(2500, meta_fields = "author")
myths_china <- gutenberg_download(15250, meta_fields = "author")
myths_japan <- gutenberg_download(4108, meta_fields = "author")
```

```{r, tidy = TRUE}
anthem_words <- anthem %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

anthem_words

bib_words <- bib %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

bib_words

sid_words <- sid %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

sid_words

myths_china_words <- myths_china %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

myths_china_words

plot_bib <- bib_words %>%
  bind_tf_idf(word, author, n) %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan", 
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

plot_physics %>% 
  group_by(author) %>% 
  top_n(15, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free") +
  coord_flip()
```

## Converting to and from non-tidy formats
### Tidying a document-term matrix
```{r, tidy = TRUE}
data("AssociatedPress", package = "topicmodels")
AssociatedPress

terms <- Terms(AssociatedPress)
head(terms)
```

```{r, tidy = TRUE}
ap_td  <- tidy(AssociatedPress)
ap_td

ap_sentiments <- ap_td %>%
  inner_join(get_sentiments("bing"), by = c(term = "word"))
ap_sentiments
```

```{r}
ap_sentiments %>%
  count(sentiment, term, wt = count) %>%
  ungroup() %>%
  filter(n >= 200) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(term = reorder(term, n)) %>%
  ggplot(aes(term, n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ylab("Contribution to sentiment") +
  coord_flip()
```
```{r}
data("data_corpus_inaugural", package = "quanteda")
inaug_dfm <- quanteda::dfm(data_corpus_inaugural, verbose = FALSE)
inaug_dfm
inaug_td <- tidy(inaug_dfm)
inaug_td
```

```{r}
inaug_tf_idf <- inaug_td %>%
  bind_tf_idf(term, document, count) %>%
  arrange(desc(tf_idf))

inaug_tf_idf
```

```{r}
year_term_counts <- inaug_td %>%
  extract(document, "year", "(\\d+)", convert = TRUE) %>%
  complete(year, term, fill = list(count = 0)) %>%
  group_by(year) %>%
  mutate(year_total = sum(count))
```

```{r}
year_term_counts %>%
  filter(term %in% c("god", "america", "foreign", "union", "constitution", "freedom")) %>%
  ggplot(aes(year, count / year_total)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ term, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  ylab("% frequency of word in inaugural address")
```

### Casting tidy text data into a matrix
```{r}
ap_td %>%
  cast_dtm(document, term, count)

ap_td %>%
  cast_dfm(document, term, count)
```
```{r}
library(Matrix)

# cast into a Matrix object
m <- ap_td %>%
  cast_sparse(document, term, count)

class(m)
dim(m)
```
```{r}
# create a dtm of Jane Austen's books
austen_dtm <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word) %>%
  cast_dtm(book, word, n)

austen_dtm
```

### Tidying corpus objects with metadata
```{r}
data("acq")
acq
# first document
acq[[1]]
acq_td <- tidy(acq)
acq_td
```

```{r}
acq_tokens <- acq_td %>%
  select(-places) %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word")

# most common words
acq_tokens %>%
  count(word, sort = TRUE)
```

```{r}
# tf-idf
acq_tokens %>%
  count(id, word) %>%
  bind_tf_idf(word, id, n) %>%
  arrange(desc(tf_idf))
```

```{r}
pacman::p_load(tm.plugin.webmining, purrr, rJava)
library(tm.plugin.webmining)
library(purrr)

company <- c("Microsoft", "Apple", "Google", "Amazon", "Facebook",
             "Twitter", "IBM", "Yahoo", "Netflix")
symbol <- c("MSFT", "AAPL", "GOOG", "AMZN", "FB", "TWTR", "IBM", "YHOO", "NFLX")

download_articles <- function(symbol) {
  WebCorpus(GoogleFinanceSource(paste0("NASDAQ:", symbol)))
}

# this doesnt work
#stock_articles <- data_frame(company = company,
#                             symbol = symbol) %>%
#  mutate(corpus = map(symbol, download_articles))
# stock_articles
```

## Topic modeling
### Latent Dirichlet allocation
```{r}
library(topicmodels)

data("AssociatedPress")
AssociatedPress
ap_lda <- LDA(AssociatedPress, k = 2, control = list(seed = 1234))
ap_lda

library(tidytext)

ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

```{r}
beta_spread <- ap_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))

beta_spread
```

```{r}
ap_documents <- tidy(ap_lda, matrix = "gamma")
ap_documents
tidy(AssociatedPress) %>%
  filter(document == 6) %>%
  arrange(desc(count))
```

### Example: the great library heist
```{r}
titles <- c("Twenty Thousand Leagues under the Sea", "The War of the Worlds",
            "Pride and Prejudice", "Great Expectations")
books <- gutenberg_works(title %in% titles) %>%
  gutenberg_download(meta_fields = "title")

# divide into documents, each representing one chapter
by_chapter <- books %>%
  group_by(title) %>%
  mutate(chapter = cumsum(str_detect(text, regex("^chapter ", ignore_case = TRUE)))) %>%
  ungroup() %>%
  filter(chapter > 0) %>%
  unite(document, title, chapter)

# split into words
by_chapter_word <- by_chapter %>%
  unnest_tokens(word, text)

# find document-word counts
word_counts <- by_chapter_word %>%
  anti_join(stop_words) %>%
  count(document, word, sort = TRUE) %>%
  ungroup()

word_counts
```

```{r}
chapters_dtm <- word_counts %>%
  cast_dtm(document, word, n)

chapters_dtm

chapters_lda <- LDA(chapters_dtm, k = 4, control = list(seed = 1234))
chapters_lda

chapter_topics <- tidy(chapters_lda, matrix = "beta")
chapter_topics
```

```{r}
top_terms <- chapter_topics %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms
```

```{r}
top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

```{r}
chapters_gamma <- tidy(chapters_lda, matrix = "gamma")
chapters_gamma <- chapters_gamma %>%
  separate(document, c("title", "chapter"), sep = "_", convert = TRUE)

chapters_gamma

chapters_gamma %>%
  mutate(title = reorder(title, gamma * topic)) %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title)
```

```{r}
chapter_classifications <- chapters_gamma %>%
  group_by(title, chapter) %>%
  top_n(1, gamma) %>%
  ungroup()

chapter_classifications

book_topics <- chapter_classifications %>%
  count(title, topic) %>%
  group_by(title) %>%
  top_n(1, n) %>%
  ungroup() %>%
  transmute(consensus = title, topic)

chapter_classifications %>%
  inner_join(book_topics, by = "topic") %>%
  filter(title != consensus)
```

```{r}
assignments <- augment(chapters_lda, data = chapters_dtm)
assignments <- assignments %>%
  separate(document, c("title", "chapter"), sep = "_", convert = TRUE) %>%
  inner_join(book_topics, by = c(".topic" = "topic"))

assignments
```

```{r}
assignments %>%
  count(title, consensus, wt = count) %>%
  group_by(title) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(consensus, title, fill = percent)) +
  geom_tile() +
  scale_fill_gradient2(high = "red", label = percent_format()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid = element_blank()) +
  labs(x = "Book words were assigned to",
       y = "Book words came from",
       fill = "% of assignments")
```
```{r}
wrong_words <- assignments %>%
  filter(title != consensus)

wrong_words %>%
  count(title, consensus, term, wt = count) %>%
  ungroup() %>%
  arrange(desc(n))

word_counts %>%
  filter(word == "flopson")
```


### Alternative LDA implementations
```{r}
library(mallet)

# create a vector with one string per chapter
collapsed <- by_chapter_word %>%
  anti_join(stop_words, by = "word") %>%
  mutate(word = str_replace(word, "'", "")) %>%
  group_by(document) %>%
  summarize(text = paste(word, collapse = " "))

# create an empty file of "stopwords"
file.create(empty_file <- tempfile())
docs <- mallet.import(collapsed$document, collapsed$text, empty_file)

mallet_model <- MalletLDA(num.topics = 4)
mallet_model$loadDocuments(docs)
mallet_model$train(100)
```

```{r}
# word-topic pairs
tidy(mallet_model)

# document-topic pairs
tidy(mallet_model, matrix = "gamma")

# column needs to be named "term" for "augment"
term_counts <- rename(word_counts, term = word)
augment(mallet_model, term_counts)
```

